---
title: "household members"
output:
  html_document:
    fig_caption: yes
    fig_height: 4
    highlight: tango
    theme: cosmo
    toc: yes
    toc_depth: 4
  pdf_document:
    fig_caption: yes
    fig_height: 3
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
rm(list = ls())
setwd("~/git/banana-phone/work")
library(dplyr)
library(tidyr)
library(ggplot2)
#library(psych)

load("clean/cleaning_all.Rdata")

# set new names
names(data2) <- new_name
```

# All household members

```{r}
# all HHM1 and HHM2 data
data_hhm <- data2 %>%
  select(c(374:375, 407:417, 405:406, 418:428))

# all ages histogram
with(data_hhm, hist(HHM1_AGE))
with(data_hhm, hist(HHM2_AGE))

```


# Household children

- need to join hhm1 and hhm2 into single dataframe

```{r}
# subset children data
hhm_ch1 <- data2 %>%
  select(c(374:375, 407:417)) %>%
  filter(HHM1_AGE < 18)
hhm_ch2 <- data2 %>%
  select(c(405:406, 418:428)) %>%
  filter(HHM2_AGE < 18)

# distribution of age
with(hhm_ch1, table(HHM1_AGE))
with(hhm_ch2, table(HHM2_AGE))

# count total number of children >18 years
hhm_ch1 %>%
  group_by(HHM1_AGE) %>%
  summarise(n = n()) %>%
  summarise(sum(n))
hhm_ch2 %>%
  group_by(HHM2_AGE) %>%
  summarise(n = n()) %>%
  summarise(sum(n))

```

Total number of children = 530


## HHM1: child 1

### Q35. What is the gender of this member of the household?  Remember, this relates to HHM1_Name who is HHM1_AGE years old.

```{r}
with(hhm_ch1, table(Q35))

```

### Q36. On average, how many days per week does this member of your household work or attend day care or school outside of your home?

```{r}
with(hhm_ch1, summary(Q36))

```

### Q37. On average, how many days per week does this member of your household participate in social activities outside of your home?

```{r}
with(hhm_ch1, summary(Q37))

```

### Q38. On average, how many days per week does this member of your household use public transportation?

```{r}
with(hhm_ch1, summary(Q38))

```

### Q39. How frequently does this member of your household visit a doctor's office for wellness appointments?

```{r}
with(hhm_ch1, table(Q39))

```

### Q40. How frequently does this member of the household get sick in a typical year?

```{r}
with(hhm_ch1, table(Q40))

```

### Q41. How many times has this member of your household had influenza or another respiratory illness in the last two years?

```{r}
with(hhm_ch1, table(Q41))

```

### Q42. Does this member of your household get an annual influenza vaccine?

```{r}
with(hhm_ch1, table(Q42))

```


## HHM2: child 2

### Q43. What is the gender of this member of the household?  Remember, this relates to HHM1_Name who is HHM1_AGE years old.

```{r}
with(hhm_ch2, table(Q43))

```


### Q44. On average, how many days per week does this member of your household work or attend day care or school outside of your home?

```{r}
with(hhm_ch2, summary(Q44))

```

### Q45. On average, how many days per week does this member of your household participate in social activities outside of your home?

```{r}
with(hhm_ch2, summary(Q45))

```

### Q46. On average, how many days per week does this member of your household use public transportation?

```{r}
with(hhm_ch2, summary(Q46))

```

### Q47. How frequently does this member of your household visit a doctor's office for wellness appointments?

```{r}
with(hhm_ch2, table(Q47))

```

### Q48. How frequently does this member of the household get sick in a typical year?

```{r}
with(hhm_ch2, table(Q48))

```

### Q49. How many times has this member of your household had influenza or another respiratory illness in the last two years?
```{r}
with(hhm_ch2, table(Q49))

```

### Q50. Does this member of your household get an annual influenza vaccine?
```{r}
with(hhm_ch2, table(Q50))

```





