---
title: "flu survey"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
```

```{r}
ds = read_csv("surveydata.csv")
```

### demographics

```{r}
ppeduc = as.data.frame(table(ds$PPEDUC))
ppeduc
q111 = as.data.frame(table(ds$Q11_1))
q111
```

```{r}
a = ggplot(ds) + scale_fill_brewer()
a + geom_bar(mapping = aes(x = ppagect4, fill = ppagect4)) + xlab("age group")
a + geom_bar(mapping = aes(x = PPEDUCAT, fill = PPEDUCAT)) + xlab("education")
a + geom_bar(mapping = aes(x = PPETHM, fill = PPETHM)) + xlab("ethnicity")
a + geom_bar(mapping = aes(x = PPGENDER, fill = PPGENDER)) + xlab("gender")
```

### survey

Q1. Before receiving this survey, did you know influenza is different from the stomach flu?
```{r, echo=FALSE}
a + geom_bar(mapping = aes(x = Q1, fill = Q1))

a + geom_bar(mapping = aes(x = Q2, fill = Q2))
a + geom_bar(mapping = aes(x = Q3, fill = Q3))
```

C. Risk of contracting influenza
Q11. How do you rate your risk of getting influenza if you visited each of the following locations?



D. Actions to avoid contracting influenza

E. Use of vaccine to reduce chance of influenza

F. Actions after contracting influenza

