---
title: "Working report"
output:
  html_document:
    fig_caption: yes
    fig_height: 4
    highlight: tango
    theme: cosmo
    toc: yes
  pdf_document:
    fig_caption: yes
    fig_height: 3
    fig_width: 5
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("~/git/banana-phone/work")
library(dplyr)
library(tidyr)
library(ggplot2)
library(psych)
#library(foreign)

# weighted data
data <- read.csv("surveydata.csv", na = c("#NULL!", "", "Refused"))
# renamed cols
data2 <- read.csv("surveydata2.csv", na = c("#NULL!", "", "Refused"))
# unweighted data -- what is the difference?
#data_unw <- read.csv("surveydata_unw.csv", na = c("#NULL!", ""))
#data_unw <- read.spss("datafile.sav", to.data.frame = TRUE)
```

#### Working analysis

```{r, eval=FALSE, include=FALSE}
# Q1 proportions
with(data, prop.table(table(Q1)))

# Q1 and Q2 counts
#with(data, by(Q1, Q2, summary))
with(data, table(Q1, Q2))

# Q1 and Q2 proportions
with(data, prop.table(table(Q1, Q2)))
with(data, prop.table(table(Q1, Q2), margin = 1))
with(data, prop.table(table(Q1, Q2), margin = 2))

# Q1 and GENDER
with(data, table(Q1, PPGENDER))
with(data, prop.table(table(PPGENDER, Q1), margin = 1))
with(data, prop.table(table(PPGENDER, Q1), margin = 2))

```


```{r, eval=FALSE, include=FALSE}
# Q7.
with(Q7, table(q, r))
# Q7. and gender
with(Q7, table(q, r, PPGENDER))

# Q33. How many people, including yourself, reside in your household?
with(data, summary(Q33))
ggplot(data, aes(x = Q33)) + geom_histogram(binwidth = 2)

# ethnicity
with(data, by(Q33, PPETHM, summary))
ggplot(data, aes(x = PPETHM, y = Q33)) + geom_boxplot() + coord_flip()


# Q2 those infected + Q3 HHC infected
with(data, table(Q2, Q3))
# by gender
test <- filter(data, Q2=='Yes', Q3=='Yes')
a = with(test, table(PPGENDER))

# chi square?
summary(with(data, table(Q2, Q3)))
with(data, table(Q2))

# remake table?
testq2 <- c(rep("Yes", 385), rep("No", 1598))
testq3 <- c(rep("Yes", 236), rep("No", 149), rep("Yes", 145), rep("No",1453))
table(testq2, testq3)
summary(table(testq2, testq3))
```


```{r, eval=FALSE, include=FALSE}
### using psych package ###
a <- describe(data)
View(a)


```




# Survey questions
### Q1. Before receiving this survey, did you know influenza is different from the stomach flu?

```{r, echo=TRUE, message=FALSE, warning=TRUE}
# Q1 table
with(data, table(Q1))
q1 <- data %>%
  group_by(Q1) %>%
  count(Q1)
ggplot(q1, aes(x = Q1, y = n, fill = Q1)) + geom_bar(stat = 'identity')


# by gender
with(data, table(Q1, PPGENDER))
q1 <- data %>%
  group_by(Q1, PPGENDER) %>%
  count(Q1, PPGENDER)
ggplot(q1, aes(x = Q1, y = n, fill = PPGENDER)) +
  geom_bar(stat = 'identity', position = position_dodge())


# by ethnicity
with(data, table(Q1, PPETHM))
q1 <- data %>%
  group_by(Q1, PPETHM) %>%
  count(Q1, PPETHM)
ggplot(q1, aes(x = Q1, y = n, fill = PPETHM)) +
  geom_bar(stat = 'identity', position = position_dodge())


# by income
with(data, table(Q1, PPINCIMP))
q1 <- data %>%
  group_by(Q1, PPINCIMP) %>%
  count(Q1, PPINCIMP)
ggplot(q1, aes(x = Q1, y = n, fill = PPINCIMP)) +
  geom_bar(stat = 'identity', position = position_dodge())
```

### Q2. Have you had an illness with influenza-like symptoms since August 2015?

```{r, echo=TRUE}
# all
with(data, table(Q2))
q2 <- data %>%
  group_by(Q2) %>%
  count(Q2)
ggplot(q2, aes(x = Q2, y = n, fill = Q2)) + geom_bar(stat = 'identity')

# by gender
with(data, table(Q2, PPGENDER))
q2 <- data %>%
  group_by(Q2, PPGENDER) %>%
  count(Q2, PPGENDER)
ggplot(q2, aes(x = Q2, y = n, fill = PPGENDER)) +
  geom_bar(stat = 'identity', position = position_dodge())

# by ethnicity
with(data, table(Q2, PPETHM))
q2 <- data %>%
  group_by(Q2, PPETHM) %>%
  count(Q2, PPETHM)
ggplot(q2, aes(x = Q2, y = n, fill = PPETHM)) +
  geom_bar(stat = 'identity', position = position_dodge())

# by income
with(data, table(Q2, PPINCIMP))
q2 <- data %>%
  group_by(Q2, PPINCIMP) %>%
  count(Q2, PPINCIMP)
ggplot(q2, aes(x = Q2, y = n, fill = PPINCIMP)) +
  geom_bar(stat = 'identity', position = position_dodge())
```

### Q3. Has any other person in your household had an illness with influenza like symptoms since August 2015?

```{r, echo=FALSE}
# all
with(data, table(Q3))
q3 <- data %>%
  group_by(Q3) %>%
  count(Q3)
ggplot(q3, aes(x = Q3, y = n, fill = Q3)) + geom_bar(stat = 'identity')

# by gender
with(data, table(Q3, PPGENDER))
q3 <- data %>%
  group_by(Q3, PPGENDER) %>%
  count(Q3, PPGENDER)
ggplot(q3, aes(x = Q3, y = n, fill = PPGENDER)) +
  geom_bar(stat = 'identity', position = position_dodge())

# by ethnicity
with(data, table(Q3, PPETHM))
q3 <- data %>%
  group_by(Q3, PPETHM) %>%
  count(Q3, PPETHM)
ggplot(q3, aes(x = Q3, y = n, fill = PPETHM)) +
  geom_bar(stat = 'identity', position = position_dodge())

# by income
with(data, table(Q3, PPINCIMP))
q3 <- data %>%
  group_by(Q3, PPINCIMP) %>%
  count(Q3, PPINCIMP)
ggplot(q3, aes(x = Q3, y = n, fill = PPINCIMP)) +
  geom_bar(stat = 'identity', position = position_dodge())
```

### Q4. Does your job require you to have a lot of contact with the public?

```{r, echo=FALSE}
# all
with(data, table(Q4))
q4 <- data %>%
  group_by(Q4) %>%
  count(Q4)
ggplot(q4, aes(x = Q4, y = n, fill = Q4)) + geom_bar(stat = 'identity')


# by gender
with(data, table(Q4, PPGENDER))
q4 <- data %>%
  group_by(Q4, PPGENDER) %>%
  count(Q4, PPGENDER)
ggplot(q4, aes(x = Q4, y = n, fill = PPGENDER)) +
  geom_bar(stat = 'identity', position = position_dodge())

# by ethnicity
with(data, table(Q4, PPETHM))
q4 <- data %>%
  group_by(Q4, PPETHM) %>%
  count(Q4, PPETHM)
ggplot(q4, aes(x = Q4, y = n, fill = PPETHM)) +
  geom_bar(stat = 'identity', position = position_dodge())

# by income 
with(data, table(Q4, PPINCIMP))
q4 <- data %>%
  group_by(Q4, PPINCIMP) %>%
  count(Q4, PPINCIMP)
ggplot(q4, aes(x = Q4, y = n, fill = PPINCIMP)) +
  geom_bar(stat = 'identity', position = position_dodge())
```

### Q5. Do you have a car that you can use to travel to work?

```{r, echo=FALSE}
# all
with(data, table(Q5))
q5 <- data %>%
  group_by(Q5) %>%
  count(Q5)
ggplot(q5, aes(x = Q5, y = n, fill = Q5)) + geom_bar(stat = 'identity')

# by gender
with(data, table(PPGENDER, Q5))
q5 <- data %>%
  group_by(Q5, PPGENDER) %>%
  count(Q5, PPGENDER)
ggplot(q5, aes(x = Q5, y = n, fill = PPGENDER)) +
  geom_bar(stat = 'identity', position = position_dodge())

# by ethnicity 
q5 <- data %>%
  group_by(Q5, PPETHM) %>%
  count(Q5, PPETHM)
ggplot(q5, aes(x = Q5, y = n, fill = PPETHM)) +
  geom_bar(stat = 'identity', position = position_dodge())

# by income 
q5 <- data %>%
  group_by(Q5, PPINCIMP) %>%
  count(Q5, PPINCIMP)
ggplot(q5, aes(x = Q5, y = n, fill = PPINCIMP)) +
  geom_bar(stat = 'identity', position = position_dodge())
```

### Q6. Do you regularly use public transportation?

```{r, echo=FALSE}
# all
with(data, table(Q6))
q6 <- data %>%
  group_by(Q6) %>%
  count(Q6)
ggplot(q6, aes(x = Q6, y = n, fill = Q6)) + geom_bar(stat = 'identity')

# by gender
# with(data, table(PPGENDER, Q6))
(q6 <- data %>%
  group_by(Q6, PPGENDER) %>%
  count(Q6, PPGENDER)
)
ggplot(q6, aes(x = Q6, y = n, fill = PPGENDER)) +
  geom_bar(stat = 'identity', position = position_dodge())

# by ethnicity 
(q6 <- data %>%
  group_by(Q6, PPETHM) %>%
  count(Q6, PPETHM)
)
ggplot(q6, aes(x = Q6, y = n, fill = PPETHM)) +
  geom_bar(stat = 'identity', position = position_dodge())

# by income 
(q6 <- data %>%
  group_by(Q6, PPINCIMP) %>%
  count(Q6, PPINCIMP)
)
ggplot(q6, aes(x = Q6, y = n, fill = PPINCIMP)) +
  geom_bar(stat = 'identity', position = position_dodge())
```

### Q7. What types of public transportation do you regularly use?

```{r, echo=FALSE}
Q7 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q7_1_Bus:Q7_otherText) %>%
  gather("q", "r", Q7_1_Bus:Q7_7_Other)

# all
with(Q7, table(q, r))
q7 <- Q7 %>%
  group_by(q, r) %>%
  count(q, r)
ggplot(q7[!is.na(q7$r), ], aes(x = r, y = n, fill = r)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~q)

# by gender
# with(Q7, table(PPGENDER, r, q))
(q7 <- Q7 %>%
  group_by(PPGENDER, q, r) %>%
  count(PPGENDER, q, r)
)
ggplot(q7[!is.na(q7$r), ], aes(x = r, y = n, fill = PPGENDER)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~q)

# by ethnicity
# with(Q7, table(PPETHM, r, q))
(q7 <- Q7 %>%
  group_by(PPETHM, q, r) %>%
  count(PPETHM, q, r)
)
ggplot(q7[!is.na(q7$r), ], aes(x = r, y = n, fill = PPETHM)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~q)

# by income
# with(Q7, table(q, r, PPINCIMP))
(q7 <- Q7 %>%
  group_by(PPINCIMP, q, r) %>%
  count(PPINCIMP, q, r)
)
ggplot(q7[!is.na(q7$r), ], aes(x = r, y = n, fill = PPINCIMP)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~q)
```

#### Q8. For what types of activities do you regularly use public transportation?
```{r}
Q8 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q8_1_Work:Q8_otherText) %>%
  gather("q", "r", Q8_1_Work:Q8_6_Other)
```

#### Q9. Do other members of your household regularly use public transportation?
```{r, echo=FALSE}


```

#### Q10. What types of public transportation do other members of your household regularly use?

Q10 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q:Q) %>%
  gather("q", "r", Q:Q)
  
```{r, echo=FALSE}


```


#### Q11. How do you rate your risk of getting influenza if you visited each of the following locations?

```{r}
Q11 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q11_1_Work:Q11_OtherText_Codes) %>%
  gather("q", "r", Q11_1_Work:Q11_11_Other)


# all
with(Q11, table(q, r))
q11 <- Q11 %>%
  group_by(q, r) %>%
  count(q, r)
ggplot(q11[!is.na(q11$r), ], aes(x = r, y = n, fill = r)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~q)

# by gender
# with(Q7, table(PPGENDER, r, q))
(q11 <- Q11 %>%
  group_by(PPGENDER, q, r) %>%
  count(PPGENDER, q, r)
)
ggplot(q11[!is.na(q11$r), ], aes(x = r, y = n, fill = PPGENDER)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~q)

# by ethnicity
# with(Q7, table(PPETHM, r, q))
(q11 <- Q11 %>%
  group_by(PPETHM, q, r) %>%
  count(PPETHM, q, r)
)
ggplot(q11[!is.na(q11$r), ], aes(x = r, y = n, fill = PPETHM)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~q)

# by income
# with(Q7, table(q, r, PPINCIMP))
(q11 <- Q11 %>%
  group_by(PPINCIMP, q, r) %>%
  count(PPINCIMP, q, r)
)
ggplot(q11[!is.na(q11$r), ], aes(x = r, y = n, fill = PPINCIMP)) +
  geom_bar(stat = 'identity', position = position_dodge()) + facet_wrap(~q)


```

#### Q12. Which of the following actions do you take to avoid getting sick?
```{r}
Q12 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, 75:91) %>%
  gather("q", "r", Q12_1_Avoid.touching.my.eyes:Q12_15_Other)

```

#### Q13. Do you get the flu vaccine?
```{r, echo=FALSE}


```

#### Q14. How much do you pay to get an influenza vaccine?
```{r}
with(data, summary(Q14))

# by gender
with(data, by(Q14, PPGENDER, summary))

```

#### Q15. Are you more likely to get a vaccine if others around you get a vaccine?
```{r, echo=FALSE}


```
#### Q16. Are you more likely to get a vaccine if others around you do not get a vaccine?
```{r, echo=FALSE}


```
#### Q17. Do you get a vaccine to protect yourself, protect others, or protect yourself and others?
```{r, echo=FALSE}


```
#### Q18. What are the reasons you would not get an influenza vaccine?

Q18 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q:Q) %>%
  gather("q", "r", Q:Q)

```{r, echo=FALSE}


```

#### Q19. Do you have health insurance?

```{r, echo=FALSE}


```
#### Q20. How effective do you think the influenza vaccine is in protecting people from becoming sick with influenza?

```{r, echo=FALSE}


```
#### Q21. Are influenza vaccines covered by your health insurance?

```{r, echo=FALSE}


```
#### Q22. Do you do any of the following when you have influenza symptoms?

Q22 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q:Q) %>%
  gather("q", "r", Q:Q)

```{r, echo=FALSE}


```

#### Q23. Which of the following actions do you take when you have influenza symptoms to avoid someone else from getting sick?

Q23 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q:Q) %>%
  gather("q", "r", Q:Q)

```{r, echo=FALSE}


```

#### Q24. What sources of information do you recall hearing or seeing about influenza outbreaks? 

Q24 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q:Q) %>%
  gather("q", "r", Q:Q)

```{r, echo=FALSE}


```

#### Q25. If you received information from the news, internet or other public media that there was an influenza outbreak in your community would you do any of the following?

Q25 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q:Q) %>%
  gather("q", "r", Q:Q)

```{r, echo=FALSE}


```

#### Q26. Does your household have children?
```{r, echo=FALSE}


```
#### Q27. What actions do you take when a child in your household has influenza symptoms?

Q27 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q:Q) %>%
  gather("q", "r", Q:Q)

```{r, echo=FALSE}


```

#### Q28. Are you a single parent?
```{r, echo=FALSE}


```
#### Q29. How do you care for a sick child?

Q29 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q:Q) %>%
  gather("q", "r", Q:Q)

```{r, echo=FALSE}


```

#### Q30. How do you care for a sick child?

Q30 <- data2 %>%
  select(PPGENDER, PPAGE, PPEDUC, PPETHM, PPINCIMP, PPWORK, Q:Q) %>%
  gather("q", "r", Q:Q)

```{r, echo=FALSE}


```

#### Q31. How many hours of screen time (time spent watching television, a computer, smartphone, iPad, etc.) do you spend each day on average when you are not sick? Enter 0 if none

```{r}
with(data, summary(Q31))

# by gender
with(data, by(Q31, PPGENDER, summary))

```

#### Q32. How many hours of screen time do you spend each day on average when you are sick? Enter 0 if none

```{r}
with(data, summary(Q32))

# by gender
with(data, by(Q33, PPGENDER, summary))

```

#### Q33. How many people, including yourself, reside in your household?

```{r}
with(data, summary(Q33))

# by ethnicity
with(data, by(Q33, PPETHM, summary))

```



# Household Members

## HHM1

#### Q35. What is the gender of this member of the household?  Remember, this relates to HHM1_Name who is HHM1_AGE years old.

```{r, echo=FALSE}


```

#### Q36. On average, how many days per week does this member of your household work or attend day care or school outside of your home?

```{r, echo=FALSE}


```

#### Q37. On average, how many days per week does this member of your household participate in social activities outside of your home?

```{r, echo=FALSE}


```

#### Q38. On average, how many days per week does this member of your household use public transportation?

```{r, echo=FALSE}


```

#### Q39. How frequently does this member of your household visit a doctor's office for wellness appointments?

```{r, echo=FALSE}


```

#### Q40. How frequently does this member of the household get sick in a typical year?

```{r, echo=FALSE}


```

#### Q41. How many times has this member of your household had influenza or another respiratory illness in the last two years?

```{r, echo=FALSE}


```

#### Q42. Does this member of your household get an annual influenza vaccine?

```{r, echo=FALSE}


```


## HHM2

#### Q43. What is the gender of this member of the household?  Remember, this relates to HHM1_Name who is HHM1_AGE years old.

```{r, echo=FALSE}


```


#### Q44. On average, how many days per week does this member of your household work or attend day care or school outside of your home?

```{r, echo=FALSE}


```

#### Q45. On average, how many days per week does this member of your household participate in social activities outside of your home?

```{r, echo=FALSE}


```

#### Q46. On average, how many days per week does this member of your household use public transportation?

```{r, echo=FALSE}


```

#### Q47. How frequently does this member of your household visit a doctor's office for wellness appointments?

```{r, echo=FALSE}


```

#### Q48. How frequently does this member of the household get sick in a typical year?

```{r, echo=FALSE}


```

#### Q49. How many times has this member of your household had influenza or another respiratory illness in the last two years?
```{r, echo=FALSE}


```

#### Q50. Does this member of your household get an annual influenza vaccine?
```{r, echo=FALSE}


```










