---
title: "flu survey"
output: 
  html_document: 
    theme: cosmo
---

```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
setwd("~/git/banana-phone/work")
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(reshape2)

data = read.csv("surveydata.csv", na = '#NULL!')
# str(data); # head(data)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# subsetting with dplyr: q.df = select(data, Q)
# renaming columns: names(dat) = c("name1", "name2", "name3")

q1.df = select(data, Q1)
q2.df = select(data, Q2)
q3.df = select(data, Q3)
q4.df = select(data, Q4)
q5.df = select(data, Q5)
q6.df = select(data, Q6)

q7.df = select(data, Q7_1:Q7_otherText)
names(q7.df) = c("Bus", "Carpool", "Subway", "Train", "Taxi", "Airplane", "Other", "Refused", "Other text")

q8.df = select(data, Q8_1:Q8_otherText)
names(q8.df) = c("Work", "School", "Shopping", "Visiting people", "Recreation", "Other", "Refused", "Other text")

q9.df = select(data, Q9)

q10.df = select(data, Q10_1:Q10_otherText)
names(q10.df) = c("Bus", "Carpool", "Subway", "Train", "Taxi", "Airplane", "Don't know", "Refused", "Other", "Refused", "Other text")

q11.df = select(data, Q11_1:Q11_OtherText_Codes)
names(q11.df) = c("Work", "Schools", "Day care", "Stores", "Restaurants", "Libraries", "Hospitals", "Doctor's office", "Public transportation", "Family or friends", "Other", "Other text")

q12.df = select(data, Q12_1:Q12_OtherText_Codes)
names(q12.df) = c()

q13.df = select(data, Q13)
q14.df = select(data, Q14)
q15.df = select(data, Q15)
q16.df = select(data, Q16)
q17.df = select(data, Q17)

q18.df = select(data, Q18_1:Q18_otherText)
names(q18.df) = c

q19.df = select(data, Q19) 
q20.df = select(data, Q20) 
q21.df = select(data, Q21) 

q22.df = select(data, Q22_1:Q22_OtherText_Codes)
names(q7.df) = c

q23.df = select(data, Q23_1:Q23_OtherText_Codes)
names(q7.df) = c

q24.df = select(data, Q24_1:Q24_otherText)
names(q7.df) = c

q25.df = select(data, Q25_1:Q25_OtherText_Codes)
names(q7.df) = c

q26.df = select(data, Q26)

q27.df = select(data, Q27_1:Q27_OtherText_Codes)
names(q7.df) = c

q28.df = select(data, Q28)

q29.df = select(data, Q29_1:Q29_OtherText_Codes)
names(q7.df) = c

q30.df = select(data, Q30_1:Q30_OtherText_Codes)


q31.df = select(data, Q31:Q31_Codes)

q32.df = select(data, Q32:Q32_Codes)

q33.df = select(data, Q33:Q33_Codes)

```

```{r, echo=FALSE, warning=FALSE}
hh.df = select(data, PRG_Q34_01:Q50) # all household questions
# summary(hh.df)

# HHM1 first household member
hhm1.df = select(data, Q35:Q42)
q35.df = select(data, Q35)
q36.df = select(data, Q36:Q36_Codes)

q37.df = select(data, Q37:Q37_Codes)

q38.df = select(data, Q38:Q38_Codes)

q39.df = select(data, Q39)
q40.df = select(data, Q40)
q41.df = select(data, Q41)
q42.df = select(data, Q42)

# HHM2 second household member
hhm2.df = select(data, Q43:Q50)
q43.df = select(data, Q43)
q44.df = select(data, Q44:Q44_Codes)

q45.df = select(data, Q45:Q45_Codes)
q46.df = select(data, Q46:Q46_Codes)
q47.df = select(data, Q47)
q48.df = select(data, Q48)
q49.df = select(data, Q49)
q50.df = select(data, Q50)
```

```{r, echo=FALSE, warning=FALSE}
# gather with tidyr: large question frames into columns
# question = gather(question, "x", "y", col:col) (i think)

q7 = gather(q7.df, "opt", "resp", 1:7)
q8 = gather(q8.df, "opt", "resp", 1:7)
q10 = gather(q10.df, "opt", "resp", 1:9)
q11 = gather(q11.df, "opt", "resp", 1:11)
q12 = gather(q12.df, "opt", "resp", 1:15)
q18 = gather(q18.df, "opt", "resp", 1:11)
q22 = gather(q22.df, "opt", "resp", 1:9)
q23 = gather(q23.df, "opt", "resp", 1:11)
q24 = gather(q24.df, "opt", "resp", 1:7)
q25 = gather(q25.df, "opt", "resp", 1:11)
q27 = gather(q27.df, "opt", "resp", 1:4)
q29 = gather(q29.df, "opt", "resp", 1:6)
q30 = gather(q30.df, "opt", "resp", 1:6)
```

## Summary tables & plots

#### Q1. Before receiving this survey, did you know influenza is different from the stomach flu?
```{r, echo=FALSE}
print(summary(q1.df))
```

#### Q2. Have you had an illness with influenza like symptoms since August 2015?
```{r, echo=FALSE}
summary(q2.df)
```

#### Q3. Has any other person in your household had an illness with influenza like symptoms since August 2015?
```{r, echo=FALSE}
summary(q3.df)
```

#### Q4. Does your job require you to have a lot of contact with the public?
```{r, echo=FALSE}
summary(q4.df)
```

#### Q5. Do you have a car that you can use to travel to work?
```{r, echo=FALSE}
summary(q5.df)
```

#### Q6. Do you regularly use public transportation?
```{r, echo=FALSE}
summary(q6.df)
```

#### Q7. What types of public transportation do you regularly use? 
```{r, echo=FALSE}
ggplot(q7) + geom_bar(aes(x = resp, fill = resp), position = "dodge") + facet_wrap(~opt)
summary(q7.df)
```

#### Q8. For what types of activities do you regularly use public transportation? 
```{r, echo=FALSE}
ggplot(q8) + geom_bar(aes(x = resp, fill = resp), position = "dodge") + facet_wrap(~opt)
summary(q8.df)
```

#### Q9. Do other members of your household regularly use public transportation?
```{r, echo=FALSE}
summary(q9.df)
```

#### Q10. What types of public transportation do other members of your household regularly use? 
```{r, echo=FALSE}
ggplot(q10) + geom_bar(aes(x = resp, fill = resp), position = "dodge") + facet_wrap(~opt)
summary(q10.df)
```

#### Q11. How do you rate your risk of getting influenza if you visited each of the following locations?
```{r, echo=FALSE}
ggplot(q11) + geom_bar(aes(x = resp, fill = resp), position = "dodge") + facet_wrap(~opt)
summary(q11.df)

```

#### Q13. Do you get the flu vaccine?
```{r, echo=FALSE}
summary(q13.df)
```

#### Q12. Which of the following actions do you take to avoid getting sick? 
```{r, echo=FALSE}
ggplot(q12) + geom_bar(aes(x = resp, fill = resp), position = "dodge") + facet_wrap(~opt)
summary(q12.df)
```

#### Q14. How much do you pay to get an influenza vaccine?
```{r, echo=FALSE}
summary(q14.df)
```

#### Q15. Are you more likely to get a vaccine if others around you get a vaccine?
```{r, echo=FALSE}
summary(q15.df)
```

#### Q16. Are you more likely to get a vaccine if others around you do not get a vaccine?
```{r, echo=FALSE}
summary(q16.df)
```

#### Q17. Do you get a vaccine to protect yourself, protect others, or protect yourself and others?
```{r, echo=FALSE}
summary(q17.df)
```

#### Q18. What are the reasons you would not get an influenza vaccine?
```{r, echo=FALSE}
ggplot(q18) + geom_bar(aes(x = resp, fill = resp), position = "dodge") + facet_wrap(~opt)
summary(q18.df)
```

#### Q19. Do you have health insurance?
```{r, echo=FALSE}
summary(q19.df)
```

#### Q20. How effective do you think the influenza vaccine is in protecting people from becoming sick with influenza?
```{r, echo=FALSE}
summary(q20.df)
```

#### Q21. Are influenza vaccines covered by your health insurance?
```{r, echo=FALSE}
summary(q21.df)
```

#### Q22. Do you do any of the following when you have influenza symptoms?
```{r, echo=FALSE}
ggplot(q22) + geom_bar(aes(x = resp, fill = resp), position = "dodge") + facet_wrap(~opt)
summary(q22.df)
```

#### Q23. Which of the following actions do you take when you have influenza symptoms to avoid someone else from getting sick?
```{r, echo=FALSE}
ggplot(q23) + geom_bar(aes(x = resp, fill = resp), position = "dodge") + facet_wrap(~opt)
summary(q23.df)
```

#### Q24. What sources of information do you recall hearing or seeing about influenza outbreaks? 
```{r, echo=FALSE}
ggplot(q24) + geom_bar(aes(x = resp, fill = resp), position = "dodge") + facet_wrap(~opt)
summary(q24.df)
```

#### Q25. If you received information from the news, internet or other public media that there was an influenza outbreak in your community would you do any of the following?
```{r, echo=FALSE}
summary(q25.df)
```

#### Q26. Does your household have children?
```{r, echo=FALSE}
summary(q26.df)
```

#### Q27. What actions do you take when a child in your household has influenza symptoms?
```{r, echo=FALSE}
summary(q27.df)
```

#### Q28. Are you a single parent?
```{r, echo=FALSE}
summary(q28.df)
```

#### Q29. How do you care for a sick child?
```{r, echo=FALSE}
summary(q29.df)
```

#### Q30. How do you care for a sick child?
```{r, echo=FALSE}
summary(q30.df)
```

#### Q31. How many hours of screen time (time spent watching television, a computer, smartphone, iPad, etc.) do you spend each day on average when you are not sick? Enter 0 if none
```{r, echo=FALSE}
summary(q31.df)
```


#### Q32. How many hours of screen time do you spend each day on average when you are sick? Enter 0 if none
```{r, echo=FALSE}
summary(q32.df)
```

#### Q33. How many people, including yourself, reside in your household?
```{r, echo=FALSE}
summary(q33.df)
```



# Household members
```{r, echo=FALSE}
summary(hhm1.df)
summary(hhm2.df)
```

## HHM1
#### Q35. What is the gender of this member of the household?  Remember, this relates to HHM1_Name who is HHM1_AGE years old.
```{r, echo=FALSE}
summary(q35.df)
```

#### Q36. On average, how many days per week does this member of your household work or attend day care or school outside of your home?
```{r, echo=FALSE}
summary(q36.df)
```

#### Q37. On average, how many days per week does this member of your household participate in social activities outside of your home?
```{r, echo=FALSE}
summary(q37.df)
```

#### Q38. On average, how many days per week does this member of your household use public transportation?
```{r, echo=FALSE}
summary(q38.df)
```

#### Q39. How frequently does this member of your household visit a doctorÕs office for wellness appointments?
```{r, echo=FALSE}
summary(q39.df)
```

#### Q40. How frequently does this member of the household get sick in a typical year?
```{r, echo=FALSE}
summary(q40.df)
```

#### Q41. How many times has this member of your household had influenza or another respiratory illness in the last two years?
```{r, echo=FALSE}
summary(q41.df)
```

#### Q42. Does this member of your household get an annual influenza vaccine?
```{r, echo=FALSE}
summary(q42.df)
```


## HHM2
#### Q43. What is the gender of this member of the household?  Remember, this relates to HHM1_Name who is HHM1_AGE years old.
```{r, echo=FALSE}
summary(q43.df)
```

#### Q44. On average, how many days per week does this member of your household work or attend day care or school outside of your home?
```{r, echo=FALSE}
summary(q44.df)
```

#### Q45. On average, how many days per week does this member of your household participate in social activities outside of your home?
```{r, echo=FALSE}
summary(q45.df)
```

#### Q46. On average, how many days per week does this member of your household use public transportation?
```{r, echo=FALSE}
summary(q46.df)
```

#### Q47. How frequently does this member of your household visit a doctorÕs office for wellness appointments?
```{r, echo=FALSE}
summary(q47.df)
```

#### Q48. How frequently does this member of the household get sick in a typical year?
```{r, echo=FALSE}
summary(q48.df)
```

#### Q49. How many times has this member of your household had influenza or another respiratory illness in the last two years?
```{r, echo=FALSE}
summary(q49.df)
```

#### Q50. Does this member of your household get an annual influenza vaccine?
```{r, echo=FALSE}
summary(q50.df)
```



#### Q1 vs. Q13 table
Knowing influenza is different from stomach flu; vs. getting the flu vaccine
```{r, echo=FALSE}
a = with(data, table(Q1, Q13))
a
summary(a)
```

```
# need to remove NA's, rename columns

# ggplot(q7) + geom_bar(aes(x = opt, fill = resp), position = "dodge")
# ggplot(data = data) + geom_bar(mapping = aes(x = Q1)) + stat_sum()
```
